---
title: "Curriculum Vitae"
---

## Education

* Ph.D in Biostatistics, University of Zurich, 03/2020--02/2023
* M.S. in Biostatistics, University of Zurich, Switzerland, 09/2018--02/2020
* B.S. in Molecular Medicine, University of Freiburg, Germany, 10/2015--06/2018

## Work experience

* 03/2024--present Assistant professor of Statistics
  * Vienna University of Economics and Business

* 03/2023--02/2024 Postdoctoral researcher 
  * University of Copenhagen
  * Collaborators: Prof. Niklas Pfister, Prof. Jonas Peters
  * Funded by a "Postdoc.Mobility" grant from the Swiss National Science
    Foundation on [Distributional Instrumental Variables Estimation
    (DIVE)](https://data.snf.ch/grants/grant/214457)

* 04/2022--07/2022 Visiting PhD student
  * University of Copenhagen
  * Supervisor: Prof. Jonas Peters

* 03/2020--02/2023: PhD candidate in Biostatistics
  * University of Zurich, Zurich University of Applied Sciences
  * Supervisors: Prof. Beate Sick, Prof. Torsten Hothorn

* 11/2018--08/2019: Research assistant
  * Functional Genomics Center Zurich, University of Zurich, ETH Zurich
  * Supervisor: Dr. Witold Wolski

* 01/2017--08/2018: Research assistant
  * University of Freiburg
  * Supervisor: Prof. Oliver Schilling

## Teaching Experience

```{r child="teaching.qmd"}

```

## Reviewing

```{r child="reviewing.qmd"}

```

## Awards and Scholarships

* 12/2022: Postdoc.Mobility grant (Swiss National Science Foundation)
  * Title: [Distributional Instrumental Variables Estimation
    (DIVE)](https://data.snf.ch/grants/grant/214457)
* 12/2021: GRC Travel Grant (University of Copenhagen, Host: Prof. Jonas Peters)
* 2015--2020: Full scholarship of the Academic Foundation of the German People
* 2015--2020: Full scholarship of the Lion's Club Viersen e.V.
  
## Languages

* English (Full professional proficiency)
* German (Native proficiency)
* Mandarin Chinese (HSK 4)
* French (Basic knowledge)

## Software

* Programming languages
  * R, Bash, Julia, Python

* Miscellaneous
  * Git, SVN, make, LaTeX, knitr, Docker

```{r child="software.qmd"}

```

## Publications

```{r child="publications.qmd"}

```

## Talks

```{r child="talks.qmd"}

```
