---
title: "Curriculum Vitae"
---

## Education

* Ph.D in Biostatistics, University of Zurich, 03/2020--02/2023
* M.S. in Biostatistics, University of Zurich, Switzerland, 09/2018--02/2020
* B.S. in Molecular Medicine, University of Freiburg, Germany, 10/2015--06/2018

## Work experience

* 03/2022--present Postdoctoral researcher 
  * University of Copenhagen
  * Collaborators: Prof. Niklas Pfister, Prof. Jonas Peters
  * Funded by postdoctoral mobility grant from the Swiss National Science Foundation

* 09/2022--02/2023 Junior editor
  * Journal of Statistical Software

* 04/2022--07/2022 Visiting PhD student
  * University of Copenhagen
  * Supervisor: Prof. Jonas Peters

* 03/2020--02/2023: PhD candidate in computational biostatistics
  * University of Zurich, Zurich University of Applied Sciences
  * Supervisor: Prof. Beate Sick, Prof. Torsten Hothorn

* 11/2018--08/2019: Research assistant
  * Functional Genomics Center Zurich, University of Zurich, ETH Zurich
  * Supervisor: Dr. Witold Wolski

* 01/2017--08/2018: Research assistant
  * University of Freiburg
  * Supervisor: Prof. Oliver Schilling

## Teaching Experience

* Student supervision
  * 3 Master students at UZH/ETHZ

* STA406 Generalized Regression (UZH, FS19/20/21)

* STA408 Statistical methods in epidemiology (UZH, SS20)

* STA402/MAT924 Likelihood inference (UZH, FS19)

* Introductory practical in physical chemistry for molecular medicine (ALU, SS18)

## Editorial responsibilities

* 09/2022--present: Junior editor for the [Journal of Statistical Software](https://www.jstatsoft.org/about/editorialTeam)

## Awards and Scholarships

* 12/2021: GRC Travel Grant (Unviersity of Copenhagen, Host: Prof. Jonas Peters)
* 2015--2020: Full scholarship of the Academic Foundation of the German People
* 2015--2020: Full scholarship of the Lion's Club Viersen e.V.
  
## Software

* Programming languages
  * R, Bash, Julia, Python

* Miscellaneous
  * Git, SVN, make, LaTeX, knitr, Docker

* Contributed R packages
  * [<bf>tramvs</bf>](https://r-forge.r-project.org/R/?group_id=1322)
  * [<bf>deepregression</bf>](https://cran.r-project.org/package=deepregression)
  * [<bf>prora</bf>](https://protviz.github.io/prora/)
  * [<bf>tramnet</bf>](https://cran.r-project.org/package=tramnet)

## Languages

* English (Full professional proficiency)
* German (Native proficiency)
* French (Basic knowledge)

## Publications

```{r child="publications.qmd"}

```

## Talks

```{r child="talks.qmd"}

```
